---
title: "CM mvpa analysis"
output: html_document
---
This document will contain the figures we publish in our countermeasures manuscript.
#Figure 1 #Figure 2 #Figure 3 #Figure 4
#Figure 5. Accuracy, confidence, d'
This should depict classification accuracy by confidence for ex>ex and ex>cm in 'late' trs, as well as tr 3
Try: 
-accuracy by confidence
-accuracy by confidence bin
-accuracy by d'
#Figure 6. Violins!
#Figure 7. Tr Sweep!











```{r}
require(gridExtra)
library(ggplot2)
library(Hmisc)

df = read.csv("/Volumes/Tyler_Drive1/CM_mvpa_results//aucSummary_first_try_hitVcr.csv", header = T)
head(df)

#add tr info
df$tr[grepl("trW1__0__0__0__0__0",df$name)]=1
df$tr[grepl("trW0__1__0__0__0__0",df$name)]=2
df$tr[grepl("trW0__0__1__0__0__0",df$name)]=3
df$tr[grepl("trW0__0__0__1__0__0",df$name)]=4
df$tr[grepl("trW0__0__0__0__1__0",df$name)]=5
df$tr[grepl("trW0__0__0__0__0__1",df$name)]=6

df$t0 = 2*(df$tr-1)

#add mask info
df$mask[grepl("roiSEPT09_MVPA_MASK_resliced4mm",df$name)]="standard mvpa mask"

#add conditions info
df$conds[grepl("conds_hitVcr_",df$name)]="hit v cr"

#add train test info
df$trte[grepl("trTe0_0_0_0_1_2_3_4_",df$name)]="CM>CM (4-fold)"
df$trte[grepl("trTe1_2_3_4_0_0_0_0_",df$name)]="EX>EX (4-fold)"
df$trte[grepl("trTe1_1_1_1_2_2_2_2_",df$name) & df$xvalIteration==2]="EX>CM (no xval)"
df$trte[grepl("trTe1_1_1_1_2_2_2_2_",df$name) & df$xvalIteration==1]="CM>EX (no xval)"

df$trte = factor(df$trte,levels=c("EX>EX (4-fold)","EX>CM (no xval)","CM>CM (4-fold)","CM>EX (no xval)"))


plotformat=theme(title= element_text(face="bold",size=15),axis.title = element_text(face="bold",size=14),axis.text=element_text(size=13))
chanceline=stat_abline(intercept=.5,slope=0,linetype="dashed")


```

Figure1.

```{r plot data}
cbPalette <- c( "#56B4E9","#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7","#999999", "#E69F00")

df_h1 = subset(df,grepl("EX>",df$trte))

h<-ggplot(df_h1, aes(x=t0)) + chanceline+geom_vline(xintercept=0, linetype="dotted")+ theme_bw() +scale_fill_manual(values=cbPalette) + scale_colour_manual(values=cbPalette)

h <- h + geom_ribbon(aes(ymin=mean_auc-sem_auc, ymax=mean_auc+sem_auc,alpha=1, fill=trte,color=trte)) + geom_line(aes(y=mean_auc,fill=trte,color=trte),linetype="dashed")
h <- h + labs(y="Classifier Performance (AUC)", x="Time post stimulus onset (s)", title="Classifier Performance Across Time") + ylim(.4, .7) +theme()

#label data
#h <- h + annotate("text", x = 6.8, y = .83, label = "CM>CM",color="red")
#h <- h + annotate("text", x = 5.8, y = .62, label = "EX>EX", color="seaFoam")
#h <- h + annotate("text", x = 5, y = .485, label = "chance")
#h <- h + annotate("text", x = 5, y = .57, label = "EX>CM", color="red") + annotate("text", x = 4.2, y = .51, label = "CM>EX", color="OliveDrab") + scale_x_continuous(breaks=seq(0,10,2))
h +plotformat
         
```

```{r load data and categorize, echo=F, results=F}
cm_df = read.csv("/Users/Jesse/fMRI/COUNTERMEASURES/Data/Functional/mvpa_results/aucSummary_reportCM_across_subs_masked.csv", header = T)
ex_df = read.csv("/Users/Jesse/fMRI/COUNTERMEASURES/Data/Functional/mvpa_results/aucSummary_reportEX_across_subs_masked.csv", header = T)
cm_df$reported = 'Countermeasures'
ex_df$reported = 'Explicit'

df = rbind(ex_df,cm_df)
df$reported=factor(df$reported,levels=c('Explicit','Countermeasures'))

#add conditions info
df$conds[grepl("conds_hitVcr_",df$name)]="hit v cr"
  
#add train test info
df$train[grepl("trAll",df$name)]="train EX and CM"
df$train[grepl("trEX",df$name)]="train EX"
df$train[grepl("trCM",df$name)]="train CM"

df$subj = sub(".*minus","",df$name)
df$subj = sub(".img","",df$subj)
```

```{r aggregate data and plot}
 #meanAndSem=function(x) c(mn = mean(x,na.rm=TRUE), se = sd(x,na.rm=T)/sqrt((sum(as.double(!is.na(x))))), max(x), min(x))
cbPalette <- c( "#56B4E9","#009E73")


df2 = aggregate(mean_auc~conds+train+reported, df, FUN=mean)
df2_h = subset(df2, train=="train EX")
df_h = subset(df, train=="train EX")

c<-with(df_h, cor.test(mean_auc[reported=="Explicit"],mean_auc[reported=="Countermeasures"],method="pearson"))

h1<-ggplot(df_h, aes(x=reported,y=mean_auc, fill=reported))+geom_violin(trim=F,alpha=.6)

h1<-h1+geom_line(aes(group=df_h$subj),color=df_h$subj,linetype="longdash")

h1<-h1+geom_point(stat='summary',fun.y='mean')

h1<-h1+theme_bw()+chanceline+labs(y="Classifier Performance (AUC)", x="Testing Data (task)", title="Classifier Performance Across Subjects")+theme(axis.ticks=element_blank(),axis.text.x=element_blank())+scale_fill_manual(values=cbPalette,name="Testing Data",breaks=c("Explicit","Countermeasures"),labels=c("Explicit","Countermeasures"))
h1+plotformat



```

```{r Across S figures}
xs_exex = read.csv("/Users/Jesse/fMRI/COUNTERMEASURES/Data/Functional/mvpa_results/acrossSs_trEXteEX_combinedFXMask_hitvcr.csv", header = T)
xs_exex$trte = "EX>EX"
xs_excm = read.csv("/Users/Jesse/fMRI/COUNTERMEASURES/Data/Functional/mvpa_results/acrossSs_trEXteCM_combinedFXMask_hitvcr.csv", header = T)
xs_excm$trte = "EX>CM"

xs_trex = rbind(xs_exex, xs_excm)
xs_trex$trte = factor(xs_trex$trte,levels=c("EX>EX","EX>CM"))

xs_trex$trW[grepl("trW1__0__0__0__0__0_",xs_trex$name)]=0
xs_trex$trW[grepl("trW0__1__0__0__0__0",xs_trex$name)]=2
xs_trex$trW[grepl("trW0__0__1__0__0__0",xs_trex$name)]=4
xs_trex$trW[grepl("trW0__0__0__1__0__0",xs_trex$name)]=6
xs_trex$trW[grepl("trW0__0__0__0__1__0",xs_trex$name)]=8
xs_trex$trW[grepl("trW0__0__0__0__0__1",xs_trex$name)]=10
xs_trex$trW[grepl("trW0____",xs_trex$name)]="late"

xs_trex$conds[grepl("conds_hitVcr_",xs_trex$name)]="hit v cr"

xs_trex$mask[grepl("roiexhitsgrcrs_AND_cmhitsgrcrs_minus",xs_trex$name)]="combined fx leave one out"
```

```{r across subs tr by tr}
xs_traggdf=aggregate(mean_auc~trW+trte+conds+mask,xs_trex,mean)

sem=aggregate(mean_auc~trW+trte+conds+mask,xs_trex,function(x) se = sd(x,na.rm=T)/sqrt((sum(as.double(!is.na(x))))))

xs_traggdf$sem_auc=sem$mean_auc


xs_traggdf_trs = subset(xs_traggdf,trW!="late")
xs_traggdf_trs$trW = as.numeric(xs_traggdf_trs$trW)

xs_tr <- ggplot(xs_traggdf_trs, aes(x=trW))+chanceline+geom_vline(xintercept=0, linetype="dotted")+ theme_bw() #+scale_fill_manual(values=cbPalette) + scale_colour_manual(values=cbPalette)
xs_tr<-xs_tr + geom_ribbon(aes(ymin=mean_auc-sem_auc, ymax=mean_auc+sem_auc,alpha=1, fill=trte,color=trte)) + geom_line(aes(y=mean_auc,fill=trte,color=trte),linetype="dashed")
xs_tr+plotformat+scale_fill_manual(values=cbPalette,name="Testing Data",breaks=c("EX>EX","EX>CM"),labels=c("Explicit","Countermeasures"))+scale_colour_manual(values=cbPalette,name="Testing Data",breaks=c("EX>EX","EX>CM"),labels=c("Explicit","Countermeasures"))+ylim(.4,.7)+ labs(y="Classifier Performance (AUC)", x="Time post stimulus onset (s)", title="Classifier Performance Across Time")+scale_x_continuous(breaks=seq(0,10,2))
```

```{r repeat for masked analyses within S}
inS_masked = read.csv("/Volumes/Tyler_Drive1/CM_mvpa_results/aucSummary__exexandexcm_lateTrs_withinS_exANDcr_hitgrcrMask.csv", header = T)
inS_masked$conds[grepl("conds_hitVcr_",inS_masked$name)]="hit v cr"
inS_masked$mask[grepl("roiexhitsgrcrs_AND_cmhitsgrcrs_minus",inS_masked$name)]="combined fx leave one out"
#add train test info
inS_masked$trte[grepl("trTe0_0_0_0_1_2_3_4_",inS_masked$name)]="CM>CM (4-fold)"
inS_masked$trte[grepl("trTe1_2_3_4_0_0_0_0_",inS_masked$name)]="EX>EX (4-fold)"
inS_masked$trte[grepl("trTe1_1_1_1_2_2_2_2_",inS_masked$name) & inS_masked$xvalIteration==2]="EX>CM (no xval)"
inS_masked$trte[grepl("trTe1_1_1_1_2_2_2_2_",inS_masked$name) & inS_masked$xvalIteration==1]="CM>EX (no xval)"

inS_masked$subj = sub(".*minus","",inS_masked$name)
inS_masked$subj = sub(".mat","",inS_masked$subj)

inS_masked$trW[grepl("trW1__0__0__0__0__0",inS_masked$name)]=0
inS_masked$trW[grepl("trW0__1__0__0__0__0",inS_masked$name)]=2
inS_masked$trW[grepl("trW0__0__1__0__0__0",inS_masked$name)]=4
inS_masked$trW[grepl("trW0__0__0__1__0__0",inS_masked$name)]=6
inS_masked$trW[grepl("trW0__0__0__0__1__0",inS_masked$name)]=8
inS_masked$trW[grepl("trW0__0__0__0__0__1",inS_masked$name)]=10
inS_masked$trW[grepl("trW0____",inS_masked$name)]="late"

inS_masked$trte = factor(inS_masked$trte, levels=c("EX>EX (4-fold)", "EX>CM (no xval)"))

inS_masked_late = subset(inS_masked, trW=="late")

c<- cor.test(inS_masked_late$mean_auc[inS_masked$trte=="EX>EX (4-fold)"], inS_masked$mean_auc[inS_masked$trte=="EX>CM (no xval)"], method = "pearson" )

h2<-ggplot(inS_masked_late, aes(x=trte,y=mean_auc, fill=trte))+geom_violin(trim=F,alpha=.6)+chanceline

h2<-h2+geom_line(aes(group=inS_masked_late$subj),color=inS_masked_late$subj,linetype="longdash")

h2<-h2+geom_point(stat='summary',fun.y='mean')

h2+theme_bw()+labs(y="Classifier Performance (AUC)", x="Testing Data (task)", title="Common FX Mask Within S")+scale_x_discrete(breaks=NULL)+theme(axis.ticks=element_blank(),axis.text.x=element_blank())+scale_fill_manual(values=cbPalette,name="Testing Data",breaks=c("EX>EX (4-fold)","EX>CM (no xval)"),labels=c("Explicit","Countermeasures"))+plotformat+ylim(0.1, 1)


inS_masked_ag = aggregate(mean_auc~trW+trte+conds+mask,inS_masked,mean)
sem=aggregate(mean_auc~trW+trte+conds+mask,inS_masked,function(x) se = sd(x,na.rm=T)/sqrt((sum(as.double(!is.na(x))))))

inS_masked_ag$sem_auc=sem$mean_auc

df_h1 = subset(inS_masked_ag,!grepl("late",inS_masked_ag$trW))
df_h1$trW = as.numeric(df_h1$trW)

  ggplot(df_h1, aes(x=trW,y=mean_auc, group=trte)) + chanceline+geom_vline(xintercept=0, linetype="dotted")+ theme_bw() + geom_ribbon(aes(ymin=mean_auc-sem_auc, ymax=mean_auc+sem_auc,alpha=1, fill=trte,color=trte), show_guide=FALSE) + geom_line(aes(y=mean_auc,fill=trte,color=trte),linetype="longdash")+ labs(y="Classifier Performance (AUC)", x="Time post stimulus onset (s)", title="Classifier Performance Across Time") + ylim(.4, .7) +theme()+scale_fill_manual(values=cbPalette) + scale_colour_manual(values=cbPalette)+plotformat

```


##Make Plots for Interaction Mask
```{r load and annotate data frame}
exex_inS_intxnMask_df = read.csv("/Volumes/Tyler_Drive1/CM_mvpa_results/aucSummary__EXEX_withinS_exgrcr_hitgrcrMask.csv", header = T)
exex_inS_intxnMask_df$trte = "EX>EX (4-fold)"
excm_inS_intxnMask_df = read.csv("/Volumes/Tyler_Drive1/CM_mvpa_results/aucSummary__EXCM_withinS_exgrcr_hitgrcrMask.csv", header = T)
excm_inS_intxnMask_df$trte = "EX>CM (no xval)"
inS_intxnMask_df = rbind(exex_inS_intxnMask_df,excm_inS_intxnMask_df)
inS_intxnMask_df$trte = factor(inS_intxnMask_df$trte,levels=c("EX>EX (4-fold)", "EX>CM (no xval)"))

#add tr info
inS_intxnMask_df$trW[grepl("trW1__0__0__0__0__0",inS_intxnMask_df$name)]=0
inS_intxnMask_df$trW[grepl("trW0__1__0__0__0__0",inS_intxnMask_df$name)]=2
inS_intxnMask_df$trW[grepl("trW0__0__1__0__0__0",inS_intxnMask_df$name)]=4
inS_intxnMask_df$trW[grepl("trW0__0__0__1__0__0",inS_intxnMask_df$name)]=6
inS_intxnMask_df$trW[grepl("trW0__0__0__0__1__0",inS_intxnMask_df$name)]=8
inS_intxnMask_df$trW[grepl("trW0__0__0__0__0__1",inS_intxnMask_df$name)]=10
inS_intxnMask_df$lateTr=FALSE
inS_intxnMask_df$lateTr[grepl("trW0____",inS_intxnMask_df$name)]=TRUE

#add mask info
inS_intxnMask_df$mask[grepl("EXgrCM",inS_intxnMask_df$name)]="intxn mask"

#add conditions info
inS_intxnMask_df$conds[grepl("conds_hitVcr_",inS_intxnMask_df$name)]="hit v cr"

#make necessary subsets
inS_intxnMask_df_late = subset(inS_intxnMask_df,lateTr == TRUE)
inS_intxnMask_df_singleTrs = subset(inS_intxnMask_df,lateTr == FALSE)
#aggregate tr by tr, mean and sem
inS_intxnMask_ag = aggregate(mean_auc~trW+trte+conds+mask,inS_intxnMask_df_singleTrs,mean)

sem=aggregate(mean_auc~trW+trte+conds+mask,inS_intxnMask_df_singleTrs,function(x) se = sd(x,na.rm=T)/sqrt((sum(as.double(!is.na(x))))))
inS_intxnMask_ag$sem_auc=sem$mean_auc

```

```{r make the plots}
ggplot(inS_intxnMask_ag, aes(x=trW,y=mean_auc, group=trte)) + chanceline+geom_vline(xintercept=0, linetype="dotted")+ theme_bw() + geom_ribbon(aes(ymin=mean_auc-sem_auc, ymax=mean_auc+sem_auc,alpha=1, fill=trte,color=trte), show_guide=FALSE) + geom_line(aes(y=mean_auc,fill=trte,color=trte),linetype="longdash")+ labs(y="Classifier Performance (AUC)", x="Time post stimulus onset (s)", title="Intxn Mask Within S") + ylim(.4, .7) +theme()+scale_fill_manual(values=cbPalette) + scale_colour_manual(values=cbPalette)+plotformat

h2<-ggplot(inS_intxnMask_df_late, aes(x=trte,y=mean_auc, fill=trte))+geom_violin(trim=F,alpha=.6)+chanceline

h2<-h2+geom_line(aes(group=inS_masked_late$subj),color=inS_masked_late$subj,linetype="longdash")

h2<-h2+geom_point(stat='summary',fun.y='mean')

h2+theme_bw()+labs(y="Classifier Performance (AUC)", x="Testing Data (task)", title="Intxn FX Mask Within S")+scale_x_discrete(breaks=NULL)+theme(axis.ticks=element_blank(),axis.text.x=element_blank())+scale_fill_manual(values=cbPalette,name="Testing Data",breaks=c("EX>EX (4-fold)","EX>CM (no xval)"),labels=c("Explicit","Countermeasures"))+plotformat+ylim(0.1, 1)

```


BEGIN PLOTS BASED ON OLD DATA
old data here means that this data was produced for the first submission of the paper. there have been subsequent modifications of the code, which mean we should rerun analyses we report.


```{r make plots for data trained within ex}
df_withinS = read.csv("/Volumes/Tyler_Drive1/CM_mvpa_results/aucSummary_exex_cmcm_hitvcr_macarthur_101014.csv", header = T)
```

```{r violin within subs}
df2 = subset(df_withinS,tr=="late")
df2$trte=factor(df2$trte,levels=c('EX>EX','EX>CM'))

c<-cor.test(df2$auc[df2$trte=="EX>EX"],df2$auc[df2$trte=="EX>CM"],method="pearson")

h2<-ggplot(df2, aes(x=trte,y=auc, fill=trte))+geom_violin(trim=F,alpha=.6)+chanceline

h2<-h2+geom_line(aes(group=df_h$subj),color=df_h$subj,linetype="longdash")

h2<-h2+geom_point(stat='summary',fun.y='mean')

h2+theme_bw()+labs(y="Classifier Performance (AUC)", x="Testing Data (task)", title="SEPT 09 Mask Within S")+scale_x_discrete(breaks=NULL)+theme(axis.ticks=element_blank(),axis.text.x=element_blank())+scale_fill_manual(values=cbPalette,name="Testing Data",breaks=c("EX>EX","EX>CM"),labels=c("Explicit","Countermeasures"))+plotformat+ylim(0.1, 1)

```


