---
title: "CM_mvpa_outline_proposal"
author: "Tyler Boyd-Meredith"
date: "November 14, 2014"
output: 
  html_document:
    toc: true
---
Proposal for outlining the mvpa section of the countermeasures manuscript.

```{r setup, echo=FALSE}
#packages
require(gridExtra)
require(plyr)
library(ggplot2)
#plot environment
cbPalette <- c( "#56B4E9","#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7","#999999", "#E69F00")
fiftyline=stat_abline(intercept=.5,slope=0,linetype="dashed")
plotformat=theme(title= element_text(face="bold",size=15),axis.title = element_text(face="bold",size=14),axis.text=element_text(size=13))
```

```{r load_data, echo=FALSE}
behav_dat_file = "~/fMRI/COUNTERMEASURES/Data/Behavioral/cm_behav_to_r.csv"
mvpa_dat_file = "~/fMRI/COUNTERMEASURES/Data/Functional/mvpa_results/aucSummaryToR__exex_excm_cmcm_hitvcr.csv"

behav_df = read.csv(behav_dat_file, header=T)
mvpa_df = read.csv(mvpa_dat_file, header=T)
```

Our question is: do countermeasures impact the ability to detect memory
#Is there signal?
First, we need to know if there is a signal discriminating hits from crs in each of our tasks. To answer this, we look at performance of two memory classifiers (hits v crs). One using 4-fold cross-validation in the explicit task, the other using the same procedure in the concealed memory task. <br>
**Predictions**:
-EX task: mean auc significantly above chance (but slightly lower than in Risman PNAS where depth of processing was likely greater at retrieval due to differences in instructions)
-CM task: mean auc significantly above chance (and higher than EX task because: a. subjects were instructed to hold stimulus in mind, b. attend and generate task are very stereotyped and map onto hit v cr discrimination)
-Weight/Importance maps will show that each classifier is relying on different information to distinguish hits from crs (prediction based on univariate maps and differences in task instructions)

#Is it usable in both tasks?
**Predictions**:
-In late trs, we will see performance at chance
-In tr-by-tr, we will see above chance performance early
-In Roi analyses, we will see above chance performance in ips and below chance in ang
